Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-23 ms.tex
updating figures

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} $\vwO$ for stellar winds ({\it solid
    blue}), SNe Ia ({\it dashed red}), MSPs ({\it solid orange}), as a
  function of $\Mbh$. Each heating source varies with the star
  formation history, which is a function of $\Mbh$--see
  appendix~\ref{app:windheat} for the detailed description of how we
  calculate $\vwO$ as a function of $\Mbh$. We also show the $\vwO$,
  resulting from stellar winds and MSPs ({\it dashed black}) and stellar
  winds, MSPs, and black hole feedback ({\it solid black}). The heating
  will have a weak dependence on the stellar density power law slope,
  $\Gamma$, since $v_{w}^{\bullet \, 2}$ depends on
  $\Gamma$. The solid black curve corresponds to $\Gamma=0.8$
  and the dash-dotted black curve corresponds to $\Gamma=0.1$.}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} $\vwO$ for stellar winds ({\it solid
    blue}), SNe Ia ({\it dashed red}), MSPs ({\it solid orange}), as a
  function of $\Mbh$. Each heating source varies with the star
  formation history, which is a function of $\Mbh$--see
  appendix~\ref{app:windheat} for the detailed description of how we
  calculate $\vwO$ as a function of $\Mbh$. We also show the $\vwO$,
  resulting from stellar winds, MSPs, and black hole feedback ({\it
    solid black}). The heating will have a weak dependence on the
  stellar density power law slope, $\Gamma$, since $v_{w}^{\bullet \,
    2}$ depends on $\Gamma$. The solid black curve corresponds to
  $\Gamma=0.8$ and the dash-dotted black curve corresponds to
  $\Gamma=0.1$. Finally the vertical dashed black line marks the value
  critical value of $\Mbh$, $M_{\rm bh, crit}$, such that... }
\end{figure}
